Digital History in Finland, 1488-1828

### 2016-06-21 inst/examples/manuscript-krakow.Rmd
started manu

---
title: "Digital History in Finland, 1488-1828"
author: "Leo Lahti"
date: "March 3, 2016"
output: markdown_document
---

```{r 20160303-init, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE}
library(stringr)
library(dplyr)
library(ggplot2)
library(bibliographica)
library(fennica)
library(sorvi)

@@

# Read data
dfo <- readRDS("df.Rds")

# Add publication decade
# TODO add already in the original preprocessed data matrix
dfo$publication_decade <- 10*floor(dfo$publication_year/10)

# Remove very early and late years
dfo <- dfo %>% filter(publication_year > 1400 & publication_year < 1911)
```

```{r 20160303-turkuvsother, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8}
# Let us focus on years 1400-1828
df <- dfo %>% filter(publication_year > 1400 & publication_year < 1829) %>%
      filter(!is.na(country)) %>%
      filter(!is.na(publication_place) & !is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01)

@@

pdf("20160303-paper.pdf", width = 12, height = 9)
print(p)
dev.off()

jpeg("20160303-paper.jpg", quality = 100, height = 480, width = 600)
print(p)
dev.off()

p <- ggplot(dfs, aes(x = publication_decade, y = titles, fill = myplace, order = -as.numeric(myplace))) +
     geom_bar(position = "stack", stat = "identity", color = "black") +
     ggtitle("Title count") +
     # scale_fill_manual(values = c("blue", "black", "darkgreen")) +
     scale_fill_grey() +
     guides(fill = guide_legend(reverse = TRUE, title = "")) +      
     xlab("Publication decade") + ylab("Title count (n)")
print(p)

pdf("20160303-titles.pdf", width = 12, height = 9)
print(p)
dev.off()

jpeg("20160303-titles.jpg", quality = 100, height = 480, width = 600)
print(p)
dev.off()
```

>>>>

---
title: "Digital History in Finland, 1488-1828"
author: "Mikko Tolonen, Jani Marjanen, Hege Roivainen, Leo Lahti"
date: "June 22, 2016"
output: markdown_document
---

```{r 201606krakow-init, echo=FALSE, message=FALSE, warning=FALSE, echo=FALSE}
library(stringr)
library(dplyr)
library(ggplot2)
library(bibliographica)
library(fennica)
library(sorvi)

@@

# Figure path
opts_chunk$set(fig.path = "figure_201606_Krakow/")

# Define time span
min.year = 1470
max.year = 1828

# Read data
fen <- readRDS("df.Rds")
kun <- readRDS("../../../kungliga/antagomir/df.Rds")

fen <- fen %>% filter(publication_year >= min.year & publication_year <= max.year)
kun <- kun %>% filter(publication_year >= min.year & publication_year <= max.year)
```

```{r 201606krakow-turkuvsother, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.height=4, fig.width=8}
df <- fen %>% 
      filter(!is.na(country)) %>%
      filter(!is.na(publication_place) & !is.na(paper.consumption.km2) & paper.consumption.km2 > -0.01)

@@

p <- ggplot(dfs, aes(x = publication_decade, y = titles, fill = myplace, order = -as.numeric(myplace))) +
     geom_bar(position = "stack", stat = "identity", color = "black") +
     ggtitle("Title count") +
     # scale_fill_manual(values = c("blue", "black", "darkgreen")) +
     scale_fill_grey() +
     guides(fill = guide_legend(reverse = TRUE, title = "")) +      
     xlab("Publication decade") + ylab("Title count (n)")
print(p)
```
